MultiDataImportPico

### 2023-12-08 Code/MultiDataImportPico.Rmd
Removed knit to html output

---
title: "MultiDataImportPico"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Mireille Savoie
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

# Load Libraries
```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(data.table)
library(photobiologyWavebands)

>>>>

---
title: "MultiDataImportPico"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Mireille Savoie
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

# Load Libraries
```{r load libraries}
# libraries; Note check actual dependencies

library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(data.table)
library(photobiologyWavebands)
